{\ttfamily oomph-\/lib} is \char`\"{}open source\char`\"{} software and may therefore be freely downloaded and distributed -- the full details are given below. To facilitate the installation of the library, the {\ttfamily oomph-\/lib} distribution includes (parts of) certain other open source libraries (Super\-L\-U, M\-E\-T\-I\-S and B\-L\-A\-S). Redistribution of these libraries with {\ttfamily oomph-\/lib} has been approved by their authors -- we suggest you get in touch with them if you wish to re-\/distribute their libraries yet again.





\subsection*{{\ttfamily oomph-\/lib's} licencing terms}

This library is free software; you can redistribute it and/or modify it under the terms of the \href{http://www.gnu.org/licenses/lgpl.html}{\tt G\-N\-U Lesser General Public License } as published by the \href{http://www.fsf.org/}{\tt Free Software Foundation} ; either version 2.\-1 of the License, or (at your option) any later version. This library is distributed in the hope that it will be useful, but W\-I\-T\-H\-O\-U\-T A\-N\-Y W\-A\-R\-R\-A\-N\-T\-Y; without even the implied warranty of M\-E\-R\-C\-H\-A\-N\-T\-A\-B\-I\-L\-I\-T\-Y or F\-I\-T\-N\-E\-S\-S F\-O\-R A P\-A\-R\-T\-I\-C\-U\-L\-A\-R P\-U\-R\-P\-O\-S\-E. See the \href{http://www.gnu.org/licenses/lgpl.html}{\tt G\-N\-U Lesser General Public License } for more details.

\par
 \par


Your use or distribution of {\ttfamily oomph-\/lib} or any derivative code implies that you agree to this License.

\par
 \par
 Copyright (c) 2006-\/2008 by \href{http://www.maths.man.ac.uk/~mheil}{\tt Matthias Heil} and \href{http://www.maths.man.ac.uk/~ahazel}{\tt Andrew L. Hazel}.





\subsection*{Licencing details for Super\-L\-U}

The {\ttfamily oomph-\/lib} distribution includes the double precision versions of the sparse direct linear solver Super\-L\-U (version 3.\-0 of the serial version and version 2.\-0 of the distributed memory parallel version). Full details of the \href{http://crd.lbl.gov/~xiaoye/SuperLU}{\tt Super\-L\-U} licence may be found at \begin{center} \href{http://crd.lbl.gov/~xiaoye/SuperLU}{\tt http\-://crd.\-lbl.\-gov/$\sim$xiaoye/\-Super\-L\-U} \end{center} 





\subsection*{Licencing details for M\-E\-T\-I\-S}

The {\ttfamily oomph-\/lib} distribution includes version 4.\-0 of George Karypis' \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt M\-E\-T\-I\-S} mesh partitioning library. Full details of the \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt M\-E\-T\-I\-S} licence may be found at \begin{center} \href{http://www-users.cs.umn.edu/~karypis/metis/}{\tt http\-://www-\/users.\-cs.\-umn.\-edu/$\sim$karypis/metis/ } \end{center} 





\subsection*{Licencing details for B\-L\-A\-S/\-L\-A\-P\-A\-C\-K}

The {\ttfamily oomph-\/lib} distribution includes the entire B\-L\-A\-S library and a few functions from L\-A\-P\-A\-C\-K. Full licencing details for the \href{http://www.netlib.org/blas/}{\tt B\-L\-A\-S library} may be found at \begin{center} \href{http://www.netlib.org/blas/}{\tt http\-://www.\-netlib.\-org/blas/ } \end{center}  Full licencing details for the \href{http://www.netlib.org/lapack/}{\tt L\-I\-B\-R\-A\-R\-Y library} may be found at \begin{center} \href{http://www.netlib.org/lapack/}{\tt http\-://www.\-netlib.\-org/lapack/ } \end{center}  





 

 \hypertarget{index_pdf}{}\section{P\-D\-F file}\label{index_pdf}
A \href{../latex/refman.pdf}{\tt pdf version} of this document is available. 